---
title: "HPU data exploration"
author: "Emma Kaz Frick"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    highlight: tango
    number_sections: false
    code_folding: hide
    df_print: paged
  word_document:
    toc: true
---

# Set up and data import

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r version-and-current-date}
R.version.string
Sys.Date()
library(tidyverse)
library(broom)
library(glue)
library(knitr)
library(mosaic)
```

## Read in and print columns

### Raw survey response data, n=160

160 observations read in. 9 non-consenting respondents were removed by
hand in the source file prior to upload.

```{r}
perceptions <- read_csv("../data/perceptions_cleaned.csv",
                        col_names=TRUE) 
head(perceptions,10)
```

### completed survey response data, n=67

```{r}
#removed any less than 100% complete
# after 100%, next listed completion level was 67% complete 
# non-consenting records were also removed by hand
percep_data <- read_csv("../data/perceptions_cleaned_incompletesremoved.csv",
                        col_names=TRUE) 
head(percep_data)
```

# Remove -99, replace with NA

```{r}
percep_data [percep_data == -99] <- NA
```

## New vectors

```{r}
percep_data |>
  mutate(
    high_confidence=
        case_when(
          sbs_confidence == 1 ~ 1,
          .default = 0)  
      ) -> percep_data_f
tail(percep_data_f,9)
```

```{r}
percep_data_f |>
  mutate(
    high_willingness=
        case_when(
          sbs_willingness == 1 ~ 1,
          .default = 0)  
      ) -> percep_data_f
tail(percep_data_f,9)
```

```{r}
percep_data_f |>
  mutate(
    age_binary=
        case_when(
          age == 6 ~ 1,
          .default = 0)  
      ) -> percep_data_f
tail(percep_data_f,9)
```

## Adding labels to ordinal & categorical values

```{r}
percep_data_f |>
  mutate(
    high_confidence_f=factor(
      high_confidence,
      levels=0:1,
      labels=c("No", "Yes")
    )
  ) |>
  mutate(
    high_willingness_f=factor(
      high_willingness,
      levels=0:1,
      labels=c("No", "Yes")
    )
  ) |>
  mutate(
    age_binary_f=factor(
      age_binary,
      levels=0:1,
      labels=c("20-59 yrs", "60+ years")
    )
  ) |>
  mutate(
    administrator_f=factor(
      professional_roles_admin,
      levels=0:1,
      labels=c("No", "Yes")
    )
  ) |>
  mutate(
    curriculum_dev_f=factor(
      professional_roles_curriculum,
     levels=0:1,
      labels=c("No", "Yes")
    )
  ) |>
  mutate(
    age_f=factor(
      age, 
      levels=2:6,
      labels=c("29 yrs or younger", "30-39 yrs", "40-49 yrs", "50-59 yrs", "60 yrs or older")
    )
  ) |>
  mutate(
    age_29drop=factor(
      age,
      levels=3:6,
      labels=c("30-39 yrs", "40-49 yrs", "50-59 yrs", "60 yrs or older")
    )
  ) |>
  mutate(
      yrs_practice_f=factor(
        yrs_practice, 
        levels=1:5,
        labels=c("less than 5 yrs", "5-10 yrs", "11-15 yrs", "16-20 yrs", "20+ yrs")
      )
  ) |>
  mutate(
      sbs_importance_f=factor(
        sbs_importance, 
        levels=1:4,
        labels=c("Critical", "Very Important", "Somewhat Important", "Not At All Important")
      )
  ) |>
  mutate(
      sbs_willingness_f=factor(
        sbs_willingness, 
        levels=1:4,
        labels=c("Very Willing", "Somewhat Willing", "Somewhat Unwilling", "Very Unwilling")
      )
  ) |>  
  mutate(
      sbs_confidence_f=factor(
        sbs_confidence, 
        levels=1:4,
        labels=c("Highly Confident", "Somewhat Confident", "Somewhat Unconfident", "Not At All Confident")
      )
  ) |>
  mutate(
    icf_f=factor(
      icf,
      levels=1:2,
      labels=c("Continue", "Exit Survey")
    )
  ) -> percep_data_f
tail(percep_data_f,10)
```

# Missingness and completion information

## Total Missing count on raw data, n=160

In the raw data there are 17,535 blank values (not including -99 values--indicating questions seen and not answered), n=160.

```{r}
    sum(is.na(perceptions))
```

## Total Missing count on cleaned data with only completed responses, n=67

There are only two missing/blank values in the cleaned data of completed responses, n=67. 
This does not include those values were a response was seen but left blank, where Qualtrics reports a -99 code.

```{r}
    sum(is.na(percep_data))
    sum(is.na(percep_data_f)) #-99 removed earlier, replaced with NA
```
 
## Number of missing values for age in raw data, n=160

```{r}
perceptions$age[perceptions$age == -99]
# dont run this: which(perceptions == -99)
```

## Total response counts

### Number of records selecting non-consent button to exit out of survey at start

Nine respondents out of 169 total chose to exit the survey at the informed script page.

```{r}
# code note: uses dplyr lib
# Counts occurrences of each value in the 'icf' column
icf_counts_accept <- percep_data_f %>%
  count(icf_f)
icf_counts_accept
```

### Counts for all responses (complete & inclomplete, but excluding non-consent)

There were a total of 160 respondents that consented to the survey.

```{r}
count(perceptions)
```

### Counts for complete responses (excluding inclomplete and non-consent)

There were 67 respondents that consented and completed the survey.

There were 93 respondents who did not complete the survey. 

```{r}
count(percep_data_f)
```

### Completion rate and duration on raw data file, n=160

Mean completion percentage was an average of 66% complete for all responses (+/- SD of 30%), n=160. 

Note: Non-consent were removed (n=9).

Mean duration of having the survey open was 2,527 seconds (or 42 minutes), SD +/- 15,136 seconds (252 minutes, or 4.2 hours), n=160. 

Median duration of having the survey open (reported so as to account for extreme outliers) was 549 seconds or 9 mins, n=160.

```{r}
perceptions |>
    summarize(
      n160_duration_minutes_mean=round(mean(duration/60, na.rm=TRUE),0),
      n160_duration_minutes_SD=round(sd(duration/60, na.rm=TRUE),0),
      n160_duration_minutes_median=round(median(duration/60,na.rm=TRUE),0),
      n160_completion_prog_percent_mean=round(mean(progress, na.rm=TRUE),0),
      n160_completion_prog_percent_SD=round(sd(progress,na.rm = TRUE),0)
    ) -> tbl_n160_completion
tbl_n160_completion
```

### Completion duration on 'completed records' data file, n=67

The following report is limited to those records that completed the survey (100% complete in completion progress variable), n=67.

The mean duration of having the survey window open was 5,369 seconds (or 90 minutes) (SD 6.4 hours), n=67.
The median duration of having the survey window open was 1,211 seconds (or 20.2 minutes) open.

```{r}
percep_data_f |>
    summarize(
      n67_duration_minutes_mean=round(mean(duration/60, na.rm=TRUE),0),
      n67_duration_minutes_SD=round(sd(duration/60, na.rm=TRUE),0),
      n67_duration_minutes_median=round(median(duration/60,na.rm=TRUE),0),
      n67_completion_prog_percent_mean=round(mean(progress, na.rm=TRUE),0),
      n67_completion_prog_percent_SD=round(sd(progress,na.rm = TRUE),0)
    ) -> tbl_n67_completion
tbl_n67_completion
```

# Demograpics

## Age distribution

### Age distribution on raw data

For the raw data, the median age group was "50-59 years". The bar chart below shows the distribution of age groups in the raw sample.

```{r}
perceptions |>
    summarize(
      raw_age_groups_median=round(median(age, na.rm=TRUE),0)
      )
```

```{r}
perceptions |>
  ggplot()+
    aes(x=age) +
    xlim(1,7) +
    geom_bar() +
    xlab("Age Group") +
    ylab("Count") +
    ggtitle("Age Distribution, Raw data") -> plot_age_raw
plot_age_raw
```

### Age distribution on cleaned data

```{r}
counts(percep_data_f$age_f)
```

```{r}
# '~ x1 + x2' for regular contingency table, 'margins=TRUE' for totals
tally(~age_f + administrator_f, margins=TRUE,data=percep_data_f)
```

```{r}
# 'x1 | x2' for col percents
tally(~age_f | administrator_f, format="percent", data=percep_data_f)
```

```{r}
# '~ x1 + x2' for regular contingency table, 'margins=TRUE' for totals
tally(~age_f + curriculum_dev_f, margins=TRUE,data=percep_data_f)
```


```{r}
tally(~age_f | curriculum_dev_f, format="percent",data=percep_data_f)
```

```{r}
# '~ x1 + x2' for regular contingency table, 'margins=TRUE' for totals
tally(~age_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```


```{r}
# 'x1 | x2' for col percents
tally(~age_f | high_confidence_f, format="percent",data=percep_data_f)
```

```{r}
# '~ x1 + x2' for regular contingency table, 'margins=TRUE' for totals
tally(~age_f + high_willingness_f, margins=TRUE,data=percep_data_f)
```

```{r}
# 'x1 | x2' for col percents
tally(~age_f | high_willingness_f, format="percent",data=percep_data_f)
```

Among completed responses, the median age group was "60 years and older". 

Values were: 2 = <=29, 3 = 30-39, 4 = 40-49, 5 = 50-59, 6 = >=60

```{r}
percep_data_f |>
    summarize(
      complete_age_groups_median=round(median(age, na.rm=TRUE),0)
      )
```

The bar chart below visualizes the distribution of age groups among complete responses. 

```{r}
percep_data_f |>
  ggplot()+
    aes(x=age_f) +
    geom_bar() + 
    xlab("Age Group") +
    ylab("Count") +
    ggtitle("Age Distribution, Among complete responses (n=67)") -> plot_n160_age
plot_n160_age
```


## Years in practice group distribution on 'completed records' data

```{r}
counts(percep_data_f$yrs_practice_f)
```

Among completed responses, the median years in practice group was "20+ years in practice". 

Values were: 1 = <5, 2 = 5-10, 3 = 11-15, 4 = 16-20, 5 = >=20

```{r}
percep_data_f |>
    summarize(
      complete_yrsprac_groups_median=round(median(yrs_practice, na.rm=TRUE),0)
      )
```

```{r}
percep_data_f |>
  ggplot()+
    aes(x=yrs_practice_f) +
    geom_bar() +
    xlab("Years in Practice Group") +
    ylab("Count") +
    ggtitle("Distribution of Years in Practice, Among complete responses (n=67)") -> plot_n67_yrs_practice
plot_n67_yrs_practice
```

## Summary of professional roles among completed responses

### Curric & admin overlap 

```{r}
counts(percep_data_f$curriculum_dev_f)
```

```{r}
counts(percep_data_f$administrator_f)
```

```{r}
counts(percep_data_f$professional_roles_didactic)
```

```{r}
counts(percep_data_f$professional_roles_clinic)
```

```{r}
counts(percep_data_f$professional_roles_preclinic)
```

```{r}
counts(percep_data_f$professional_roles_accreditation)
```



36% of sample were curric dev, 45% were administrators
If you are in curric dev you are more likely to be an admin. 18/67 were both admin and curric devs.
If you were not an admin, you probably werent a curric dev (6/67 were curric dev but NOT admin).  

```{r}
tally(~curriculum_dev_f + administrator_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~curriculum_dev_f + administrator_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```


Response counts for professional roles (multiple check box), n=67: 

\ 50 didactic 

\ 65 clinical 

\ 33 preclinical 

\ 30 administrative 

\ 24 curriculum development 

\ 25 research 

\ 6 other (free text prompt)

\ Values were -99 = seen and not answered; 0 = not checked, 1 = checked.


```{r}
percep_data_f |>
count(professional_roles_didactic) -> tbl_dida
print(tbl_dida)
```

```{r}
percep_data_f |>
count(professional_roles_clinic) -> tbl_clin
print(tbl_clin)
```

```{r}
percep_data_f |>
count(`professional_roles_preclinic`) -> tbl_pre
print(tbl_pre)
```

```{r}
percep_data_f |>
count(professional_roles_admin) -> tbl_admin
print(tbl_admin)
```

```{r}
percep_data_f |>
count(professional_roles_curriculum) -> tbl_curr
print(tbl_curr)
```

```{r}
percep_data_f |>
count(professional_roles_research) -> tbl_res
print(tbl_res)
```

```{r}
percep_data_f |>
count(professional_roles_other) -> tbl_other
print(tbl_other)
```

```{r}
bind_cols(tbl_dida, tbl_clin, tbl_pre, tbl_admin, tbl_curr, tbl_res, tbl_other) -> tbl_prof_roles
glimpse(tbl_prof_roles)
```

# Summary Questions on SBS Importance, Willingness, and Confidence

## Rating Social and behavioral science Importance

```{r}
counts(percep_data_f$sbs_importance_f)
```

Median response on importance of SBS was a score of 1 = "critical importance".

```{r}
percep_data_f |>
summarize(median(sbs_importance,na.rm = TRUE))
```

```{r}
percep_data_f |>
  ggplot()+
    aes(x=sbs_importance_f) +
    geom_bar() +
    xlab("Rating the Importance of SBS") +
    ylab("Count") +
    ggtitle("'Importance of SBS' Distribution, Among Complete responses (n=67)") -> plot_n67_sbs_importance
plot_n67_sbs_importance
```

## Rating Social and behavioral science Willingness

```{r}
counts(percep_data_f$sbs_willingness_f)
```

Median response on willingness to implement SBS into practice was a score of 1 = "very willing".

```{r}
percep_data_f |>
summarize(median(sbs_willingness,na.rm = TRUE))
```

```{r}
percep_data_f |>
  ggplot()+
    aes(x=sbs_willingness_f) +
    geom_bar() +
    xlab("Rating Willingness to integrate SBS") +
    ylab("Count") +
    ggtitle("'Willingness to integrate SBS' Distribution, Among Complete responses (n=67)") -> plot_n67_sbs_willingness
plot_n67_sbs_willingness
```

## Rating Social and behavioral science Confidence

```{r}
counts(percep_data_f$sbs_confidence_f)
```

Median response on their confidence in integrating SBS was a score of 2 = "Somewhat confident".

```{r}
percep_data_f |>
summarize(median(sbs_confidence,na.rm = TRUE))
```

```{r}
percep_data_f |>
  ggplot()+
    aes(x=sbs_confidence_f) +
    geom_bar() +
    xlab("Rating Confidence in Integrating SBS") +
    ylab("Count") +
    ggtitle("'Confidence in integrating SBS' Distribution, Among Complete responses (n=67)") -> plot_n67_sbs_confidence
plot_n67_sbs_confidence
```

# Summary of CE sources

Response count for SBS CE type (multiple check boxes), n=67:

\ 43 Attending workshops or conferences 

\ 38 Participating in online courses or webinars

\ 32 Reading academic journals or publications 

\ 46 Engaging in discussions with colleagues or peers 

\ 23 Seeking mentorship or guidance from experts

\ 4 other (free text prompt) 

\ 5 none - do not engage with SBS CE

\ 1 viewed but did not complete this question (-99 value)

\ Values were -99 = seen and not answered; 0 = not checked, 1 = checked.

```{r}
percep_data_f |>
count(`ce_Attending workshops or conferences`) -> tbl_ce_wksp
print(tbl_ce_wksp)
```

```{r}
percep_data_f |>
count(`ce_Participating in online courses or webinars`) -> tbl_ce_web
print(tbl_ce_web)
```

```{r}
percep_data_f |>
count(`ce_Reading academic journals or publications`) -> tbl_ce_pub
print(tbl_ce_pub)
```

```{r}
percep_data |>
count(`ce_Engaging in discussions with colleagues or peers`) -> tbl_ce_peer
print(tbl_ce_peer)
```

```{r}
percep_data_f |>
count(`ce_Seeking mentorship or guidance from experts`) -> tbl_ce_exp
print(tbl_ce_exp)
```

```{r}
percep_data_f |>
count(ce_other) -> tbl_ce_other
print(tbl_ce_other)
```

```{r}
percep_data_f |>
count(ce_none) -> tbl_ce_none
print(tbl_ce_none)
```

```{r}
bind_cols(tbl_ce_wksp,tbl_ce_web,tbl_ce_pub,tbl_ce_peer,tbl_ce_exp,tbl_ce_other,tbl_ce_none) -> tbl_ce_types
print(tbl_ce_types)
```

## Table of CE Types (Counts)

```{r}
df_ce_counts <- data.frame(
  Category=c("Conference", "Webinar", "Journal", "Peers", "Experts", "Other","None"),
  count=c(43,38,32,46,23,4,1))
print(df_ce_counts)
```

```{r}
#pivot table for CE vars
percep_data_f |>
  select(`ce_Attending workshops or conferences`,
         `ce_Participating in online courses or webinars`,
         `ce_Reading academic journals or publications`,
         `ce_Engaging in discussions with colleagues or peers`,
         `ce_Seeking mentorship or guidance from experts`,
         ce_other,
         ce_none) -> df_ce
head(df_ce,10)
```

## Pie Chart of CE Types (Counts)

```{r}
t(df_ce_counts) -> ce_counts_transpose
ce_counts_transpose
```

```{r}
df_pie_ce <- data.frame(
  Category=c("Conference", "Webinar", "Journal", "Peers", "Experts", "Other", "None"),
  count=c(43,38,32,46,23,4,1)
)
ggplot(df_pie_ce,
       aes(x="",
         y=count,
         fill=Category)) +
  geom_bar(stat="identity",
           width=1) +
  scale_fill_brewer(palette="Set2") +
  coord_polar(theta="y") +
  theme_void() +
  labs(title="Sources of Continuing Education for SBS Topics") -> plot_n67_pie_ce
plot_n67_pie_ce
```


## Table of Role Types (counts)

```{r}
df_role_counts <- data.frame(
  Category=c("Didactic", "Clinic", "Preclinic", "Administrative", "Curriculum Development", "Research","Other"),
  count=c(50,65,33,30,24,25,6))
print(df_role_counts)
```


## Pie Chart of Role Types (Counts)

```{r}
t(df_role_counts) -> df_role_counts_transpose
df_role_counts_transpose
```

```{r}
df_pie_role <- data.frame(
  Category=c("Didactic", "Clinic", "Preclinic", "Administrative", "Curriculum Development", "Research", "Other"),
  count=c(50,65,33,30,24,25,6))
ggplot(df_pie_role,
       aes(x="",
         y=count,
         fill=Category)) +
  geom_bar(stat="identity",
           width=1) +
  scale_fill_brewer(palette="Set2") +
  coord_polar(theta="y") +
  theme_void() +
  labs(title="Professional Roles Held") -> plot_n67_pie_role
plot_n67_pie_role
```

# 2x2 Tables

## Confidence X Willingness

```{r}
tally(~high_confidence_f + high_willingness_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~high_confidence_f + high_willingness_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

### Admin X Willingness

```{r}
tally(~administrator_f + high_willingness_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~administrator_f + high_willingness_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

### Curriculum X Willingness

```{r}
tally(~curriculum_dev_f + high_willingness_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~curriculum_dev_f + high_willingness_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

### Age X Willingness

```{r}
tally(~age_binary_f + high_willingness_f, margins=TRUE,data=percep_data_f)
```

```{r}
tally(~age_f + high_willingness_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~age_29drop + high_willingness_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

```{r}
xchisq.test(~age_binary_f + high_willingness_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

### Admin X Confidence

```{r}
tally(~administrator_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~administrator_f + high_confidence_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

### Curriculum X Confidence

```{r}
tally(~curriculum_dev_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~curriculum_dev_f + high_confidence_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

### Age X Confidence

```{r}
tally(~age_binary_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```

```{r}
tally(~age_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```

```{r}
xchisq.test(~age_binary_f + high_confidence_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```


```{r}
xchisq.test(~age_29drop + high_confidence_f,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

## CE Counts filtered by Willingness

```{r}
percep_data_f |>
  select(high_willingness_f, `ce_Attending workshops or conferences`,`ce_Participating in online courses or webinars`,`ce_Reading academic journals or publications`,`ce_Engaging in discussions with colleagues or peers`,`ce_Seeking mentorship or guidance from experts`,ce_other, ce_none) -> df_ce_groupby_willingness
df_ce_groupby_willingness
```


# Grouping by Confidence Level

```{r}
# '~ x1 + x2' for regular contingency table, 'margins=TRUE' for totals
tally(~high_willingness_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```

```{r}
# '~ x1 + x2' for regular contingency table, 'margins=TRUE' for totals
tally(~administrator_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```

```{r}
# '~ x1 + x2' for regular contingency table, 'margins=TRUE' for totals
tally(~curriculum_dev_f + high_confidence_f, margins=TRUE,data=percep_data_f)
```

```{r}
percep_data_f |>
	count(high_confidence_f) |>
  	mutate(total=sum(n)) |>
  	mutate(pct=round(100*n/total)) |>
	  mutate(pct=glue("{pct}% ({n}/{total})")) |>
	  select(-n, -total) -> tbl_count_conf
tbl_count_conf
```

## Confidence and CE
CE categories:
\ - ce_Attending workshops or conferences	
\ - ce_Participating in online courses or webinars	
\ - ce_Reading academic journals or publications	
\ - ce_Engaging in discussions with colleagues or peers	
\ - ce_Seeking mentorship or guidance from experts	
\ - ce_other	
\ - ce_none

### CE Counts filtered by Confidence

```{r}
percep_data_f |>
  select(high_confidence_f, `ce_Attending workshops or conferences`,`ce_Participating in online courses or webinars`,`ce_Reading academic journals or publications`,`ce_Engaging in discussions with colleagues or peers`,`ce_Seeking mentorship or guidance from experts`,ce_other, ce_none) -> df_ce_groupby_confidence
df_ce_groupby_confidence
```

### Attending workshops or conferences

```{r}
plot_bar_ce_con <- select(
    percep_data_f,`ce_Attending workshops or conferences`, high_confidence_f) |>
  filter(`ce_Attending workshops or conferences`!= -99) |>
  ggplot() +
    aes(`ce_Attending workshops or conferences`, 
        fill=high_confidence_f) +
    geom_bar()
plot_bar_ce_con
```

```{r}
tally(~ `ce_Attending workshops or conferences` + 
        high_confidence, 
      margins=TRUE, 
      data=percep_data_f)
```

```{r}
tally(~`ce_Attending workshops or conferences` +
        high_confidence,
      format="percent",
      data=percep_data_f)
```

```{r}
xchisq.test(~`ce_Attending workshops or conferences` +
        high_confidence,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

```{r}
mosaicplot(~`ce_Attending workshops or conferences` +
             high_confidence_f,
           color=TRUE,
           data=percep_data_f)
```

### Participating in online courses or webinars

```{r}
plot_bar_ce_web <- select(
    percep_data_f,`ce_Participating in online courses or webinars`, high_confidence_f) |>
  filter(`ce_Participating in online courses or webinars`!= -99) |>
  ggplot() +
    aes(`ce_Participating in online courses or webinars`, 
        fill=high_confidence_f) +
    geom_bar()
plot_bar_ce_web
```

```{r}
tally(~ `ce_Participating in online courses or webinars` + 
        high_confidence, 
      margins=TRUE, 
      data=percep_data_f)
```

```{r}
tally(~`ce_Participating in online courses or webinars` +
        high_confidence,
      format="percent",
      data=percep_data_f)
```

```{r}
xchisq.test(~`ce_Participating in online courses or webinars` +
        high_confidence,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

```{r}
mosaicplot(~`ce_Participating in online courses or webinars` +
             high_confidence_f,
           color=TRUE,
           data=percep_data_f)
```

### Reading academic journals or publications

```{r}
plot_bar_ce_pub <- select(
    percep_data_f,`ce_Reading academic journals or publications`, high_confidence_f) |>
  filter(`ce_Reading academic journals or publications`!= -99) |>
  ggplot() +
    aes(`ce_Reading academic journals or publications`, 
        fill=high_confidence_f) +
    geom_bar()
plot_bar_ce_pub
```

```{r}
tally(~ `ce_Reading academic journals or publications` + 
        high_confidence, 
      margins=TRUE, 
      data=percep_data_f)
```

```{r}
tally(~`ce_Reading academic journals or publications` +
        high_confidence,
      format="percent",
      data=percep_data_f)
```

```{r}
xchisq.test(~`ce_Reading academic journals or publications` +
        high_confidence,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

```{r}
mosaicplot(~`ce_Reading academic journals or publications` +
             high_confidence_f,
           color=TRUE,
           data=percep_data_f)
```

## Confidence and Role

### Admin confidence

```{r}
plot_bar_admin <- ggplot(
  percep_data_f,
  aes(
    administrator_f, fill=high_confidence_f)) +
  geom_bar()
plot_bar_admin
```

```{r}
tally(~administrator_f + 
        high_confidence, 
      margins=TRUE, 
      data=percep_data_f)
```

```{r}
tally(~administrator_f +
        high_confidence,
      format="percent",
      data=percep_data_f)
```

```{r}
xchisq.test(~administrator_f +
        high_confidence,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

```{r}
mosaicplot(~administrator_f +
             high_confidence_f,
           color=TRUE,
           data=percep_data_f)
```

### Curriculum Developer Confidence

```{r}
plot_bar_curr <- ggplot(
  percep_data_f,
  aes(
    curriculum_dev_f, fill=high_confidence_f)) +
  geom_bar()
plot_bar_curr
```

```{r}
tally(~curriculum_dev_f + 
        high_confidence, 
      margins=TRUE, 
      data=percep_data_f)
```

```{r}
tally(~curriculum_dev_f +
        high_confidence,
      format="percent",
      data=percep_data_f)
```

```{r}
xchisq.test(~curriculum_dev_f +
        high_confidence,
      data=percep_data_f,
      correct=FALSE,
      simulate.p.value = TRUE)
```

```{r}
mosaicplot(~curriculum_dev_f +
             high_confidence_f,
           color=TRUE,
           data=percep_data_f)
```

# Grouping by Curriculum Developer Role

```{r}
percep_data_f |>
	count(curriculum_dev_f) |>
  	mutate(total=sum(n)) |>
  	mutate(pct=round(100*n/total)) |>
	  mutate(pct=glue("{pct}% ({n}/{total})")) |>
	  select(-n, -total) -> tbl_count_curric
tbl_count_curric
```

# Grouping by Admin Role

```{r}
percep_data_f |>
	count(administrator_f) |>
  	mutate(total=sum(n)) |>
  	mutate(pct=round(100*n/total)) |>
	  mutate(pct=glue("{pct}% ({n}/{total})")) |>
	  select(-n, -total) -> tbl_count_admin
tbl_count_admin
```

# SBS Special Population Questions 

## Frequency Section

Q8 Frequency: An estimate of how often you encounter the topic in patient care Please rate the frequency of providing care for patients with the following social or behavioral health factors:

Less than annually (1)
Annually (2)
Quarterly (3)
Monthly (4)
Weekly (5)
Daily (6)

### Freq: Low Health Literacy (LHL) Population

```{r}
percep_data_f |>
    summarize(
      all_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

#### Freq: LHL by Confidence

Only by high confidence: 

```{r}
percep_data_f |>
  filter(high_confidence_f!="No") |>
    summarize(
      highconf_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

Only by less than high confidence:  

```{r}
percep_data_f |>
  filter(high_confidence_f!="Yes") |>
    summarize(
      lowconf_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

#### Freq: LHL by Willingness

Only by high Willingness: 

```{r}
percep_data_f |>
  filter(high_willingness_f !="No") |>
    summarize(
      highwill_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

Only by less than high Willingness: 

```{r}
percep_data_f |>
  filter(high_willingness_f !="Yes") |>
    summarize(
      lowwill_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

#### Freq: LHL by Age

Only by Older respondents (60+): 

```{r}
percep_data_f |>
  filter(age_binary_f !="20-59 yrs") |>
    summarize(
      older_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

Only by Younger respondents (20-59): 

```{r}
percep_data_f |>
  filter(age_binary_f !="60+ years") |>
    summarize(
      younger_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

#### Freq: LHL by Adminitrator Role

Only by Administrators: 

```{r}
percep_data_f |>
  filter(administrator_f !="No") |>
    summarize(
      yesadmin_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

Only by non-Administrators: 

```{r}
percep_data_f |>
  filter(administrator_f !="Yes") |>
    summarize(
      notadmin_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

#### Freq: LHL by Curriculum Role

Only by Curriculum Developers: 

```{r}
percep_data_f |>
  filter(curriculum_dev_f !="No") |>
    summarize(
      yescurric_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```

Only by non-Curriculum Developers: 

```{r}
percep_data_f |>
  filter(curriculum_dev_f !="Yes") |>
    summarize(
      notcurric_median_freq_lowhealthlit=round(median(freq_lowhealthlit,na.rm=TRUE),0))
```


## Difficulty Section

Q18 Difficulty: Your perceived difficulty of asking, evaluating, and integrating the topic into patient care Please rate the difficulty of providing care for patients with the following social or behavioral health factors:

Not at all (1)
Low (2)
Moderate (3)
High (4)

### Diff: Low Health Literacy (LHL) Population

```{r}
percep_data_f |>
    summarize(
      all_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

#### Diff: LHL by Confidence

Only by high confidence: 

```{r}
percep_data_f |>
  filter(high_confidence_f!="No") |>
    summarize(
      highconf_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

Only by less than high confidence:  

```{r}
percep_data_f |>
  filter(high_confidence_f!="Yes") |>
    summarize(
      lowconf_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

#### Diff: LHL by Willingness

Only by high Willingness: 

```{r}
percep_data_f |>
  filter(high_willingness_f !="No") |>
    summarize(
      highwill_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

Only by less than high Willingness: 

```{r}
percep_data_f |>
  filter(high_willingness_f !="Yes") |>
    summarize(
      lowwill_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

#### Diff: LHL by Age

Only by Older respondents (60+): 

```{r}
percep_data_f |>
  filter(age_binary_f !="20-59 yrs") |>
    summarize(
      older_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

Only by Younger respondents (20-59): 

```{r}
percep_data_f |>
  filter(age_binary_f !="60+ years") |>
    summarize(
      younger_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

#### Diff: LHL by Administrator Role

Only by Administrators: 

```{r}
percep_data_f |>
  filter(administrator_f !="No") |>
    summarize(
      yesadmin_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

Only by non-Administrators: 

```{r}
percep_data_f |>
  filter(administrator_f !="Yes") |>
    summarize(
      notadmin_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

#### Diff: LHL by Curriculum Role

Only by Curriculum Developers: 

```{r}
percep_data_f |>
  filter(curriculum_dev_f !="No") |>
    summarize(
      yescurric_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

Only by non-Curriculum Developers: 

```{r}
percep_data_f |>
  filter(curriculum_dev_f !="Yes") |>
    summarize(
      notcurric_median_diff_lowhealthlit=round(median(diff_lowhealthlit,na.rm=TRUE),0))
```

## Importance/impact Section

Q19 Importance: The perceived impact of the topic on patient care outcomes (e.g., their significance) Please rate the importance of providing care for patients with the following social or behavioral health factors:

Not at all (1)
Low (2)
Moderate (3)
High (4)


## Ability Section

Q20 Ability: Your ability level to ask, evaluate, and integrate the topic into patient care Please rate your ability level to provide care for patients with the following social or behavioral health factors:

Poor (1)
Adequate (2)
Good (3)
Excellent (4)

# Remove -99, replace with NA

```{r}
#percep_data_f[percep_data_f == -99] <- NA
```

# Write to file

```{r}
#write.csv(percep_data_f, "../data/percep_data_export.csv", row.names = FALSE)
```

